Implementing simplified INLA into `aghq`

### 2022-10-27 src/dev_sinla/sinla.Rmd
Cautionary tale: if you change the data and you're using a non-adaptive quadrature rule you're going to have a bad time

```{r}
spacing <- 0.05
x_grid <- seq(from = 0.5, to = 3.5, by = spacing)
x_grid_length <- length(x_grid)

@@

@@

```{r}
spacing <- 0.05
x_grid <- seq(from = 0.5, to = 3.5, by = spacing)
```

>>>>

```{r}
spacing <- 0.05
x_grid <- seq(from = -5, to = 5, by = spacing)
x_grid_length <- length(x_grid)

@@

# Extension beyond empirical Bayes

In Sections \@ref(gaussian-marginal) and \@ref(full-laplace) when calculating $\tilde p(x_i \, | \, y)$ we fixed $\theta = \hat \theta$ ($K = 1$, empirical Bayes) rather than integrating $\theta$ out ($K > 1$).
In this section we will use `ahgq` to integrate over $\theta$.

## Marginal of joint Gaussian approximation

```{r}
#' To-do
```

## Full Laplace approximation

```{r}
#' To-do
```

@@

```{r}
x_grid
```
